Viscous Erosion in Porous Media

### 2018-01-18 docs/methods/erosion_methods.tex
Working on paper

Interestingly, a brief look at Fig.~\ref{shrink_intface}(a) reveals that the spacing between successive interfaces becomes larger as the body shrinks, suggesting that the overall shear stress is growing. Of course, such a relationship is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu V / L$, since stress is inversely proportional to body size. In two dimensions, though, this law is modified. The correct modification can be inferred

Interestingly, the spacing between successive interfaces in Fig.~\ref{shrink_intface}(a) becomes larger as time progresses

@@

\vsp{30}
Later, as a segue to discuss the vanishing of area, I can point out that the interface spacing becomes greater at later times in Fig. 5a.

\subsubsection{The vanishing rate of area}
In three-dimensional Stokes flow, the shear stress vanishes as
\begin{equation}
\tauD{3} \sim \mu V/L
\end{equation}
However, this law must be modified for 2D flow, which represents 3D
bodies of large extent. As the body vanishes, the walls have an ever
decreasing influence. Thus, the stress must be consistent with
free-space slender-body theory as it vanishes. The stress law consistent
with slender body theory (a long cylinder held perpendicular to a flow)
is
\begin{equation}
\tauD{2} \sim \frac{\mu V}{L \log(W/L)}
\end{equation}
% Could include 4 \pi factor, which is appropriate for a circular cylinder

>>>>

\todo[inline]{I am not sure if $V$ has been defined previously. If not, need to define it.}

Interestingly, a brief look at Fig.~\ref{shrink_intface}(a) reveals that the spacing between successive interfaces becomes larger as the body shrinks, suggesting that the overall shear stress is growing. Of course, such a relationship is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu V / L$, since stress is inversely proportional to body scale $L$. This law must be modified in 2D, though. The modification is made non-trivial by subtleties associated with the Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory. For a slender body in flow perpendicular to its long-axis $W \gg L$, the drag is proportional to $\mu V W/ \log(W/L)$. This relationship implies that, for a 2D cross-section perpendicular to the long axis, the stress can be estimated by
\begin{equation}
\tau \sim \frac{\mu V}{L \log(W/L)}
\end{equation}
In interpreting our 2D simulations, we will treat $W$ as fixed (and must remember the requirement $W \gg L$).

\vsp{30}

@@

\subsubsection{The vanishing rate of area}
